---
title: "C- Archive - check high resolution model reproducibility"
author: "swann floc'hlay"
date: '2023-03-16'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dev-check-model-reproducibility-highres}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Checking reproducibility of FishMap results

 <!-- this vignette is generated from dev/dev_check_model_reproducibility_highres.Rmd, make your edit on this original file -->

This notebook gather the analysis performed in order to compare the output of the original FishMap `main.R` script between Client and ThinkR. We will compare the results obtained with identical seeds following the execution of the script `dev/run_main_and_save_output.R`.

Here, we use **high resolution parameters** :

  * `k = 0.75`
  * `month_start <- 10`
  * `month_end <- 12`

## Executing `main.R`

We generate the outputs on ThinkR machine.
> make sure your .Renviron variables `FISHMAP_UPDATE_OUTPUTS` and `FISHMAP_OUTPUT_DIR` are correctly set

```{r eval=FALSE}
# Generate results (model files are compiled)
source(here::here("dev", "run_main_and_save_output.R"))
```

Executing this code results in four outputs to be compared.

```{r}
output_dir <- Sys.getenv("FISHMAP_OUTPUT_DIR")
list.files(path = file.path(output_dir))
```

To check whether the seed is effectively making the output reproducible, we will run a second time `main.R` with the same seed.

```{r  message=FALSE, warning=FALSE, results = 'hide'}
# Change output dir to avoid overriding previous run
Sys.setenv(FISHMAP_OUTPUT_DIR = "~/shared/outputs_fishmap_highres_rerun")

# Run main.R a second time (model files are already compiled from first run)
source(here::here("dev", "run_main_and_save_output.R"))
```

_Note_: model fit is performed in 186 steps in this run.

We list the resulting output files.

```{r}
thinkr1_output_dir <- file.path("~","shared","outputs_fishmap_highres_rerun")

thinkr1_output <- paste0(
  list.files(
    path = thinkr1_output_dir,
    full.names = TRUE
  ),
  collapse = "\n"
)

glue::glue("The paths to ThinkR's second run output files are :\n {thinkr1_output}")

thinkr2_output_dir <- file.path("~","shared","outputs_fishmap_highres")

thinkr2_output <- paste0(
  list.files(
    path = thinkr2_output_dir,
    full.names = TRUE
  ),
  collapse = "\n"
)

glue::glue("The paths to ThinkR's first run output files are :\n {thinkr2_output}")
```

## Checking seed reproducibility

In order to contrast output files from both ThinkR runs, we will use the package `{waldo}`.

```{r}
# list of output fiiles to contrast
files_to_contrast <- list.files(path = file.path(thinkr1_output_dir))

# running waldo on each files comparing thinkR runs
purrr::map(
  .x = files_to_contrast,
  ~ waldo::compare(
    x = readRDS(
      file.path(thinkr1_output_dir, .x)
    ),
    y = readRDS(
      file.path(thinkr2_output_dir, .x)
    )
  )
) %>% setNames(files_to_contrast)
```
Both ThinkR outputs are identical. We will use one of them to now compare with the Client's output.

## Loading Client's output

We now load the outputs generated from Clients (BA and JC) in a temporary folder.

```{r}
# Create tmp folder to store Client output
tmp_folder <- tempfile(pattern = "fishmap_highres")
dir.create(tmp_folder)

# Download and unzip JC highres outputs from Git repo
jc_zip_file_url <- "https://github.com/balglave/FishMap/files/10970908/outputs_fishmap_highres.zip"
download.file(
  url = jc_zip_file_url,
  destfile = file.path(tmp_folder, "jc_output.zip")
)

unzip(
  zipfile = file.path(tmp_folder, "jc_output.zip"),
  exdir = file.path(tmp_folder, "jc_output")
)

jc_output_dir <- file.path(tmp_folder, "jc_output", "outputs_fishmap_highres")

jc_output <- paste0(
  list.files(
    path = jc_output_dir,
    full.names = TRUE
  ),
  collapse = "\n"
)

glue::glue("The paths to Juliette's output files are :\n {jc_output}")

# Download and unzip BA highres outputs from Git repo
ba_zip_file_url <- "https://github.com/balglave/FishMap/files/10982408/outputs_fishmap_highres.zip"
download.file(
  url = ba_zip_file_url,
  destfile = file.path(tmp_folder, "ba_output.zip")
)

unzip(
  zipfile = file.path(tmp_folder, "ba_output.zip"),
  exdir = file.path(tmp_folder, "ba_output")
)

ba_output_dir <- file.path(tmp_folder, "ba_output","outputs_fishmap_highres")

ba_output <- paste0(
  list.files(
    path = ba_output_dir,
    full.names = TRUE
  ),
  collapse = "\n"
)

glue::glue("The paths to Baptiste's output files are :\n {ba_output}")
```


## Contrasting files

Results between ThinkR and Client's are not perfectly identical. 

**Important note** : To compare numerical results we will set a tolerance in numerical differences to **10e-4**.

We find differences in function code present in the outputs (see section on `obj_inputs.rds`). This might indicate a difference in **package version**. cf. `sessionInfo()` provided by Clients.

### Create contrast function

We will use again `{waldo}` within a function to display the exact differences for each file.

```{r}
# Create a function to explore waldo's output file by file between ThinkR and Baptiste + Juliette outputs

compare_output_file <- function(file_name, author) {
  if (author == "juliette") {
    client_output_dir <- jc_output_dir
  } else if (author == "baptiste") {
    client_output_dir <- ba_output_dir
  } else {
    stop("author must be either juliette or baptiste")
  }

  # running waldo on one file (thinkR ~ client)
  message(glue::glue("contrasting output of {file_name} between thinkr and {author}"))
  compare_author <- waldo::compare(
    x = readRDS(
      file.path(client_output_dir, file_name)
    ),
    y = readRDS(
      file.path(thinkr1_output_dir, file_name)
    ),
    x_arg = author,
    y_arg = "thinkr",
    max_diffs = 100,
    tolerance = 10e-4
  )

  return(compare_author)
}
```

### Contrasting `converge_output.rds` output

```{r}
compare_output_file(file_name = "converge_output.rds", author = "baptiste")
compare_output_file(file_name = "converge_output.rds", author = "juliette")
```

### Contrasting `opt_output.rds` output

```{r}
compare_output_file(file_name = "opt_output.rds", author = "baptiste")
compare_output_file(file_name = "opt_output.rds", author = "juliette")
```

### Contrasting `report_output.rds` output

```{r}
compare_output_file(file_name = "report_output.rds", author = "baptiste")
compare_output_file(file_name = "report_output.rds", author = "juliette")
```

### Contrasting `obj_input.rds` output


```{r}
compare_output_file(file_name = "obj_input.rds", author = "juliette")
```

We encounter an error when contrasting the `fn` and `env` element of the `obj_input.rds` object between Baptiste's version and ThinkR's version. We run `{waldo}` element by element except for the object of class `environment`, with a specific parameter (`ignore_function_env = TRUE`) that ignore function environment comparison and allows the comparison to succeed. This error might come from a difference in package version (cf. comment at the beginning of section).

```{r}
file_name <- "obj_input.rds"
author <- "baptiste"
client_output_dir <- ba_output_dir

message(glue::glue("contrasting elemts of {file_name} element by element between thinkr and {author}"))

client_obj <- readRDS(
    file.path(client_output_dir, file_name)
  )

thinkr_obj <- readRDS(
    file.path(thinkr1_output_dir, file_name)
  )

# select elements of list that are not a env class
list_is_env <- purrr::map_lgl(client_obj, ~ inherits(.x, "environment"))
list_names_not_env <- names(client_obj)[!list_is_env]

purrr::map(
  .x = list_names_not_env,
  ~ waldo::compare(
  x = client_obj[[.x]],
  y = thinkr_obj[[.x]],
  x_arg = author,
  y_arg = "thinkr",
  tolerance = 10e-6,
  max_diffs = 100,
  ignore_function_env = TRUE
)
) %>% setNames(list_names_not_env)

```

```{r}
# delete temporary folder
unlink(tmp_folder)
```


```{r eval=FALSE}
# knit the Rmd as a compiled Rmd in vignettes
knitr::knit(
  input = here::here("dev/archive/dev_check_model_reproducibility_highres.Rmd"),
  output = here::here("vignettes/dev-check-model-reproducibility-highres.Rmd")
)
```
