---
title: "C - Archive - check high resolution model reproducibility with same package version"
author: "swann floc'hlay"
date: '2023-03-16'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dev-check-model-reproducibility-highres-same-pkg-version}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Checking reproducibility of FishMap results

 <!-- this vignette is generated from dev/dev_check_model_reproducibility_highres_same_pkg_version.Rmd, make your edit on this original file -->

This notebook gather the analysis performed in order to compare the output of the original FishMap `main.R` script between Client and ThinkR. We will compare the results obtained with identical seeds following the execution of the script `dev/run_main_and_save_output.R`.

Here, we use **high resolution parameters** :

  * `k = 0.75`
  * `month_start <- 10`
  * `month_end <- 12`

We use similar **package versions** for Client and ThinkR outputs :

  * Baptiste : `R version 4.2.3` ; `TMB_1.9.2` ; `INLA_22.12.16`
  * ThinkR [swann] : `R version 4.2.0` ; `TMB_1.9.0` ; `INLA_22.12.16`

## Executing `main.R`

We generate the outputs on ThinkR machine. Make sure your .Renviron variables `FISHMAP_UPDATE_OUTPUTS` and `FISHMAP_OUTPUT_DIR` are correctly set.

```{r  message=FALSE, warning=FALSE, results = 'hide'}
# Run main.R a second time (model files are already compiled from first run)
source(here::here("dev", "run_main_and_save_output.R"))
```

We list the resulting output files.

```{r}
thinkr1_output_dir <- file.path("~","shared","outputs_fishmap_highres_rerun")

thinkr1_output <- paste0(
  list.files(
    path = thinkr1_output_dir,
    full.names = TRUE
  ),
  collapse = "\n"
)

glue::glue("The paths to ThinkR's second run output files are :\n {thinkr1_output}")
```

## Loading Client's output

We now load the outputs generated from Clients (BA) in a temporary folder.

```{r}
# Create tmp folder to store Client output
tmp_folder <- tempfile(pattern = "fishmap_highres")
dir.create(tmp_folder)

# Download and unzip BA highres outputs from Git repo
ba_zip_file_url <- "https://github.com/balglave/FishMap/files/11011699/outputs_fishmap_highres_updatepkg.zip"
download.file(
  url = ba_zip_file_url,
  destfile = file.path(tmp_folder, "ba_output.zip")
)

unzip(
  zipfile = file.path(tmp_folder, "ba_output.zip"),
  exdir = file.path(tmp_folder, "ba_output")
)

ba_output_dir <- file.path(tmp_folder, "ba_output", "outputs_fishmap_highres_updatepkg")

ba_output <- paste0(
  list.files(
    path = ba_output_dir,
    full.names = TRUE
  ),
  collapse = "\n"
)

glue::glue("The paths to Baptiste's output files are :\n {ba_output}")
```

## Contrasting files

Results between ThinkR and Client's are not perfectly identical.

**Important note** : To compare numerical results at two precision levels, we will consecutively set a tolerance in numerical differences to **1e-4** (as used in the other comparison vignettes) and **1e-6**.

**Conclusion** : 

  * We find **no differences** in numerical outputs when we use a numerical tolerance of **1e-4**.
  * We detect differences in numerical outputs with a tolerance of **1e-6**
  * We find a non-numerical difference in the `fn` element of the `obj_input.rds` file for both tolerance thresholds
  * Numerical differences between Client and ThinkR outputs exist but are all inferior to 1e-4.

### Create contrast function

We will use again `{waldo}` within a function to display the differences for each file. We will adapt the `tolerance` parameter to adjust numerical comparison threshold.

```{r}
# Create a function to explore waldo's output file by file between ThinkR and Baptiste outputs

compare_output_file <- function(file_name, tolerance) {
  # define client output dir
  client_output_dir <- ba_output_dir

  # running waldo on one file (thinkR ~ client)
  message(glue::glue("contrasting output of {file_name} between thinkr and baptiste with a numerical tolerance of {tolerance}"))
  compare_author <- waldo::compare(
    x = readRDS(
      file.path(client_output_dir, file_name)
    ),
    y = readRDS(
      file.path(thinkr1_output_dir, file_name)
    ),
    x_arg = "baptiste",
    y_arg = "thinkr",
    max_diffs = 100,
    tolerance = tolerance
  )

  return(compare_author)
}
```

### Contrasting all outputs at `1e-4` numerical tolerance

We first make the comparison for each file with a tolerance of `1e-4`.

```{r}
compare_output_file(file_name = "converge_output.rds", tolerance = 1e-4)
compare_output_file(file_name = "opt_output.rds", tolerance = 1e-4)
compare_output_file(file_name = "report_output.rds", tolerance = 1e-4)
compare_output_file(file_name = "obj_input.rds", tolerance = 1e-4)
```
With a numerical tolerance of `1-e4`, the outputs between ThinkR and Baptiste are identical, with the exception of the `fn` object in `obj_inputs.rds`, which was also reported when contrasting Juliette's outputs. All numerical outputs are identical at **1e-4** numerical tolerance.

### Contrasting `converge_output.rds` output at `1e-6` numerical tolerance

We will now run the same comparison for each file, with a more stringent numerical tolerance of `1e-6`.

```{r}
compare_output_file(file_name = "converge_output.rds", tolerance = 1e-6)
```

### Contrasting `opt_output.rds` output at `1e-6` numerical tolerance

```{r}
compare_output_file(file_name = "opt_output.rds", tolerance = 1e-6)
```

### Contrasting `report_output.rds` output at `1e-6` numerical tolerance

```{r}
compare_output_file(file_name = "report_output.rds", tolerance = 1e-6)
```

### Contrasting `obj_input.rds` output at `1e-6` numerical tolerance


```{r}
compare_output_file(file_name = "obj_input.rds", tolerance = 1e-6)
```

```{r}
# delete temporary folder
unlink(tmp_folder)
```


```{r eval=FALSE}
# knit the Rmd as a compiled Rmd in vignettes
knitr::knit(
  input = here::here("dev/archive/dev_check_model_reproducibility_highres_same_pkg_version.Rmd"),
  output = here::here("vignettes/dev-check-model-reproducibility-highres-same-pkg-version.Rmd")
)
```
