---
title: "flat_run_main_and_save_output.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Execute `main.R` with timer, seed and data storage

Make sure you have the two following environment variables in your `.Renviron` file :

* `FISHMAP_OUTPUT_DIR` : path to the directory to store the model output, it will be created if it does not exist

* `FISHMAP_UPDATE_OUTPUTS` : logical, enable outputs to be saved if sets to `TRUE`

To update your `.Renviron` file, you can run the `usethis::edit_r_environ()` command which will directly open the file in edit mode. Once your changes saved, you will need to restart your R session.

```{r vign-renviron, eval = FALSE}
FISHMAP_OUTPUT_DIR="~/shared/outputs_fishmap"
FISHMAP_UPDATE_OUTPUTS=TRUE
```

To execute `main.R` and store its output, execute the following command.
This script will execute `main.R` with a seed to secure reproducibility, it will report time of execution per step and store the data in the folder specified by the environment variable.

```{r vign-run_main_and_save_output, eval = FALSE}
source(here::here("dev","run_main_and_save_output.R"))
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_run_main_and_save_output.Rmd",
               vignette_name = "dev - execute main",
               check = FALSE)

# To perform check, please go to `dev/0_dev_history.Rmd` and run the section `Use every time needed`
```

