---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FishMap

<!-- badges: start -->
[![.github/workflows/R-CMD-check](https://github.com/balglave/FishMap/actions/workflows/.github/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/balglave/FishMap/actions/workflows/.github/workflows/R-CMD-check.yaml)
[![R-CMD-check](https://github.com/balglave/FishMap/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/balglave/FishMap/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of FishMap is to ...

## Installation

You can install the development version of FishMap from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("balglave/FishMap")
```

## Documentation

Full documentation website on: https://balglave.github.io/FishMap

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# library(FishMap)
## basic example code
```


## Code of Conduct

Please note that the FishMap project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
