---
title: "Development actions history"
output: html_document
editor_options: 
  chunk_output_type: console
---

All commands that you use to use when developing packages...

# First time just after creating the project

- Fill the following chunk to create the DESCRIPTION of your package

```{r description, eval=FALSE}
# Done in "dev/dev_history_package.Rmd"
```

# Start using git

```{r, eval=FALSE}
usethis::use_git()
# Deal with classical files to ignore
usethis::git_vaccinate()
# Use main for primary branch
usethis::git_default_branch_rename()
```

# Set extra sources of documentation

```{r, eval=FALSE}
# Install a first time
remotes::install_local()
# README
usethis::use_readme_rmd()
# Code of Conduct
usethis::use_code_of_conduct("contact@fake.com")
# NEWS
usethis::use_news_md()
```

**From now, you will need to "inflate" your package at least once to be able to use the following commands. Let's go to your flat template, and come back here later if/when needed.**


# Package development tools
## Use once

```{r, eval=FALSE}
# Pipe
usethis::use_pipe()
usethis::use_data_raw()

# package-level documentation
usethis::use_package_doc()

# GitHub
# Add your credentials for GitHub
usethis::create_github_token()
gitcreds::gitcreds_set()

# _All-in-one share of your package and its documentation on GitHub
fusen::init_share_on_github()

# _Or one step at a time
# Send your project to a new GitHub project (included in `init_share_on_github()`)
usethis::use_github()

# Set Continuous Integration
# _GitHub (included in `init_share_on_github()`)
usethis::use_github_action("check-standard")
usethis::use_github_action("pkgdown")
usethis::use_github_action("test-coverage")

# ignore data and model files in build
usethis::use_build_ignore(c("inst/model.so","inst/model.o"))
```

## Use everytime needed

```{r}
# Simulate package installation
pkgload::load_all()

# Extract all pakg liste in r_script_orig
extra_pkg <- attachment::att_from_rscripts(path = c("inst/original_scripts", "dev/r_scripts_orig/function/","dev/r_scripts_orig/"))

# add splancs
extra_pkg <- c("splancs", "rgdal")

# Generate documentation and deal with dependencies
attachment::att_amend_desc(extra.suggests = extra_pkg, must.exist = FALSE)
#remotes::install_deps(upgrade = "never")

# Check the package with FishMap execution in CRAN conditions
# install.packages('checkhelper', repos = 'https://thinkr-open.r-universe.dev')
checkhelper::check_as_cran()

# Check the package with FishMap execution
devtools::check()

# Check the package without FishMap execution
devtools::check(args = c("--no-vignettes"),
                 build_args = c("--no-build-vignettes"))

# Add a new flat template
fusen::add_flat_template("add")
```

If you update the package and it results in expected changes to output values, you should update the test files to enable the comparison checks to succeed.
To do so, you should update the files present in the `inst/expect_outputs` with your updated output files. Make sure your files follow the same naming convention. These files are part of the package, you should avoid using very large files.

```{r}
# Update expect output files in inst/ folder with local output files
file_to_update <- c("part1_output0.25.rds")
output_dir <- Sys.getenv("FISHMAP_OUTPUT_DIR")
test_dir <- here::here("tests","testthat")

file.copy(from = file.path(output_dir, file_to_update),
          to = test_dir,
          overwrite = TRUE)
```

# Share the package

```{r}
# set and try pkgdown documentation website locally
usethis::use_pkgdown()
pkgdown::build_site()

# build the tar.gz with vignettes to share with others
devtools::build(vignettes = TRUE)

# Share your package and its documentation on GitHub
# usethis::create_github_token()
# gitcreds::gitcreds_set()
fusen::init_share_on_github()
```

