---
title: "Dev history - Package"
output: 
  html_document:
    toc: true
    toc_depth: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = FALSE
  )
```

In this document, you will find the useful steps/commands to start the development of a package (structure, documentation, ...)

# At the beggining of the developments
## Set the dev tools

### Add git templates

```{r}
# GitLab MR and git commit templates
# lozen::add_git_templates()
```

### Add kit package

```{r}
# lozen::add_kit_package(type = c("package", "deliverables"))
# lozen::add_kit_project()
```

### Create a `inst` dir

```{r}
dir.create("inst")
```

### Hide some files in .Rbuildignore and .gitignore

```{r}
usethis::use_build_ignore("dev")
# usethis::use_build_ignore("ci/lib")
# usethis::use_build_ignore("rsconnect")

usethis::use_git_ignore("docs/")
# usethis::use_git_ignore("rsconnect/")
usethis::git_vaccinate()
usethis::use_git_ignore(c(".DS_Store", ".Rproj.user", ".Rdata", ".Rhistory", ".httr-oauth"))
```

### Add some required packages

```{r}
# Pipe ----
usethis::use_pipe()
# _Tests ----
usethis::use_testthat()
```

### Set the CI

```{r}
# GitHub Actions ----
usethis::use_github_action("check-standard")
# usethis::use_github_action("pkgdown")
#  _Add remotes::install_github("ThinkR-open/thinkrtemplate") in this action
# usethis::use_github_action("test-coverage")
```

## Add general information/documentation about the package

### Update DESCRIPTION

```{r}
library(desc)
unlink("DESCRIPTION")
# Utiliser `lozen::get_author()` pour aider à remplir DESCRIPTION'
lozen::get_author()

my_desc <- description$new("!new")
my_desc$set_version("0.0.0.9000")
my_desc$set(Package = "FishMap")
my_desc$set(Title = "Spatial-temporal Models For Fish Distributions with 'TMB'")
my_desc$set(Description = "Combine survey and VMS data to model the distribution of fish using 'TMB' models.")
my_desc$set(
  "Authors@R",
  'c(
    person("Baptiste", "Alglave", email = "baptiste.alglave@univ-ubs.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0000-0000-0000")),
    person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", role = c("aut"), comment = c(ORCID = "0000-0002-1565-9313")),
    person(given = "Swann", family = "Floc\'hlay", role = "aut", email = "swann@thinkr.fr", comment = c(ORCID = "0000-0003-1477-830X")),
  person(given = "Ifremer", role = "cph")
)'
)
my_desc$set("VignetteBuilder", "knitr")
my_desc$del("Maintainer")
my_desc$del("URL")
my_desc$del("BugReports")
my_desc$write(file = "DESCRIPTION")
```

### Licence

```{r}
# usethis::use_proprietary_license("ThinkR")
usethis::use_mit_license("Baptiste Alglave")
```

### README

```{r}
# usethis::use_readme_rmd()
```

### NEWS

```{r}
usethis::use_news_md()
```

### Code of conduct

```{r}
usethis::use_code_of_conduct(contact = "baptiste.alglave@univ-ubs.fr")
```

### Contributing guide

```{r}
usethis::use_tidy_contributing()
```

### Package-level documentation

```{r}
usethis::use_package_doc()
```

## Tools to help to resolve issues

```{r}
# Get global variables
checkhelper::print_globals()
checkhelper::find_missing_tags()
# Hexadecimal translation of an accent - if there are notes about non ASCII characters
stringi::stri_trans_general("é", "hex")
```

