---
title: "flat_main.Rmd"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

```{r message=FALSE}
library(dplyr)
library(INLA)
library(ggplot2)
library(sf)
library(stringr)
library(tidyr)
library(TMB)
library(tictoc)
library(testthat)
```

# `main.R`

This vignette runs a toy example of the FishMap spatio-temporal model. The execution comprises three steps : data preparation, model fitting and graph generation.

## part1: Data preparation

### `fm_load_data()` : prepare and load model inputs

This function Prepare all the necessary output for the model fitting. It will filter and shape the observation data (VMS and scientific). It will generate the spatial mesh for the study domain. All outputs are reported as part of a named list.

```{r preex-fm_load_data}
# run part 1
survey_data_file <- system.file("original_data",
                                "Solea_solea",
                                "survey_data.Rdata",
                                package = "FishMap"
                                )

vmslogbook_data_file <- system.file("original_data",
                                "Solea_solea",
                                "vmslogbook_data.Rdata",
                                package = "FishMap"
                                )

study_domain_file <- system.file("original_data",
                                "Solea_solea",
                                "study_domain.Rdata",
                                package = "FishMap"
                                )

fm_data_inputs <- fm_load_data(species = "Solea_solea",
                         fleet = c("OTB_DEF_>=70_0","OTB_CEP_>=70_0","OTT_DEF_>=70_0"),
                         fitted_data = "biomass",
                         survey_data_file = survey_data_file,
                         vmslogbook_data_file = vmslogbook_data_file,
                         study_domain_file = study_domain_file,
                         year_start = 2018,
                         year_end = 2018,
                         month_start = 11,
                         month_end = 11,
                         time_step = "Month",
                         k = 0.25,
                         grid_xmin = -6,
                         grid_xmax = 0,
                         grid_ymin = 42,
                         grid_ymax = 48)
```

## part2: fit model

### `fm_fit_model()`: compile model and fit to data

This function will fit the model to the observation data. It will compile the model cpp file. It will fit the model to the input data generated from `fm_load_data()` and provide the results as a named list.

  
```{r preex-fm_fit_model}
# run part 2
fm_model_results <- fm_fit_model(fm_data_inputs = fm_data_inputs,
                                 SE = 1,
                                 data_source = 1,
                                 data_obs = 2,
                                 samp_process = 0,
                                 b_constraint = 2,
                                 cov_samp_process = 0,
                                 biomass_temporal = 1,
                                 sampling_temporal = 0,
                                 lf_link = 0,
                                 ref_data = "com",
                                 EM = "est_b",
                                 month_ref = 1)
```


## part3: generate output graphs

### `fm_generate_graphs()` : generate output graphs

This function will generate graphs of the model predictions. It will use as input the data generated from `fm_fit_model()` and provide the predictive plot within a named list. Is the sampling process is activated (`samp_process = 1`), an additionnal graphic for eta result will be generated.

```{r preex-fm_generate_graphs}
# run part 3
fm_generate_graphs(fm_model_results = fm_model_results)
```

```{r tests-complete_pipeline}
test_that("Main functions work together", {
  
  # Set up params for the model
  
  # run part1
  survey_data_file <- system.file("original_data",
                                  "Solea_solea",
                                  "survey_data.Rdata",
                                  package = "FishMap"
  )
  
  vmslogbook_data_file <- system.file("original_data",
                                      "Solea_solea",
                                      "vmslogbook_data.Rdata",
                                      package = "FishMap"
  )
  
  study_domain_file <- system.file("original_data",
                                   "Solea_solea",
                                   "study_domain.Rdata",
                                   package = "FishMap"
  )
  
  fm_data_inputs <- fm_load_data(species = "Solea_solea",
                                 fleet = c("OTB_DEF_>=70_0","OTB_CEP_>=70_0","OTT_DEF_>=70_0"),
                                 fitted_data = "biomass",
                                 survey_data_file = survey_data_file,
                                 vmslogbook_data_file = vmslogbook_data_file,
                                 study_domain_file = study_domain_file,
                                 year_start = 2018,
                                 year_end = 2018,
                                 month_start = 11,
                                 month_end = 11,
                                 time_step = "Month",
                                 k = 0.25,
                                 grid_xmin = -6,
                                 grid_xmax = 0,
                                 grid_ymin = 42,
                                 grid_ymax = 48)
  
  
  #'@description Testing that fm_data_inputs return a named list for the next function
  test_list <- is.list(fm_data_inputs)
  test_name <- length(names(fm_data_inputs)) != 0 
  
  expect_true(test_list & test_name)
  
  #'@descripton Testing if `fm_fit_model` always work
  result_fit_model <- try(
    fm_fit_model(fm_data_inputs = fm_data_inputs,
                 SE = 1,
                 data_source = 1,
                 data_obs = 2,
                 samp_process = 0,
                 b_constraint = 2,
                 cov_samp_process = 0,
                 biomass_temporal = 1,
                 sampling_temporal = 0,
                 lf_link = 0,
                 ref_data = "com",
                 EM = "est_b",
                 month_ref = 1), 
    silent = TRUE)
  
  expect_true(
               !inherits(result_fit_model, "try-error"), 
               label = "`fm_fit_model` generate a error. Please check the core function or the returned objet of `fm_load_data`. Running function"
  )
  
  
  #'@descripton Testing if `fm_fit_model` always work
  result_graph <- try(fm_generate_graphs(result_fit_model), silent = TRUE)
  
  expect_true(
               !inherits(result_graph, "try-error"), 
               label = "`fm_generate_graphs` generate a error. Please check the core function or the returned objet of `fm_fit_model`. Running function"
  )
  
  #'@description testing output of `fm_generate_graphs`
  expect_type(result_graph, "list")
  expect_s3_class(result_graph[["pred_plot"]], "ggplot")
  
})
```

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_main.Rmd", check = FALSE,
               vignette_name = "user - running fishmap")
# To perform check, please go to `dev/0_dev_history.Rmd` and run the section `Use everytime needed`
```
